Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 Lemmas.tex
moved Zhao to appendix, fixed typos

>>>>

The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
concentration inequality due to \cite{zhao2016adaptive},
given as Lemma~\ref{lem:ACI-inequality}.

\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
\label{lem:ACI-inequality}
Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
(We allow $J$ to take the value $\infty$,
defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
Define 
$g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.
Then, 
$\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}$.
\end{lemma}

### 2018-02-17 algorithm_general.tex
moved Zhao to appendix, fixed typos

We begin by bounding the length of any phase, which will support bounding
the regret of early rounds
(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the Appendix.

@@

We now state the key technical lemma captures the intuition that
the estimates of the arms' attribute vectors become
more accurate with increasing phases $s$.

@@

The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
concentration inequality due to \cite{zhao2016adaptive},
given as Lemma~\ref{lem:ACI-inequality}.

\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
\label{lem:ACI-inequality}
Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
(We allow $J$ to take the value $\infty$,
defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
Define 
$g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.
Then, 
$\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}$.
\end{lemma}

>>>>

We begin by bounding the length of any phase, which will support bounding
the regret of early rounds
(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the appendix.

@@

We now state the key technical lemma which captures the intuition that
the estimates of the arms' attribute vectors become
more accurate with increasing phases $s$.

@@
